|

### 2020-01-09 _other/tikz/tree/fs_tikz_gametree.tex
apm ex-mode :q :w, game tree continued

\subsection{Nodes Only}

When developing trees, to simply the problem, first just draw nodes and branches, no text, no benidng, no coloring.

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child
child{
    [grow=right]
    child
    child{
        [grow=right]
        child
        child
        child
        child
        child
        }
    child
    }
child;
\end{tikzpicture}
\end{center}

>>>>

\subsection{Develop Tree Outline}

\subsubsection{Nodes Only}

Draw nodes and branches, no text, no bending, no coloring.

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child
child{
    [grow=right]
    child
    child{
        [grow=right]
        child
        child
        child
        child
        }
    child
    }
child;
\end{tikzpicture}
\end{center}

\subsubsection{First Two Nodes with Continuous Curved Bend Right}

Add Continuous bending curves.

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    child{
        [black] node(21)[]{}
    }
    child{
        [grow=right]
        child
        child
        child
        child
    }
    child{
        [black] node(23)[]{}
    }
}
child{
    [black] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\end{tikzpicture}
\end{center}

\subsubsection{Extend Middle node Rightward}

Continuous bending exceed middle node, now offset middle node.

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child{ 
    [black] node(11)[]{}
}
child{
    [grow=right]
    [white] node(12)[solid node, xshift=7.5, yshift=0]{}
    child{
        [black] node(21)[]{}
    }
    child{
        [grow=right]
        [white] node(22)[solid node, xshift=7.5, yshift=0]{}
        child {
            [black] node(31)[]{}
        }
        child{
            [black] node(32)[]{}
        }
        child{
            [black] node(33)[]{}   
        }
        child{
            [black] node(34)[]{}
        }
    }
    child{
        [black] node(23)[]{}
    }
}
child{
    [black] node(13)[]{}
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\draw[dotted, line width=0.35mm]
    (0) to (12);
\draw[dotted, line width=0.35mm]
    (12) to (22);
\end{tikzpicture}
\end{center}

### 2020-01-09 nontex/install/linux/fn_vim.Rmd
apm ex-mode :q :w, game tree continued

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Remap Keys
"""""""""""""""""""""""""""""""""""""""""""""""""
" esc in insert mode
" inoremap jj <esc>
```

>>>>

" Rmd Syntax Highlighting, Nvim-R renders
Plug 'jalvesaq/Nvim-R' 
Plug 'vim-pandoc/vim-rmarkdown'
Plug 'vim-pandoc/vim-pandoc-syntax'

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Remap Keys
"""""""""""""""""""""""""""""""""""""""""""""""""
" esc in insert mode
inoremap jj <Esc>
```

### 2020-01-09 nontex/install/windows/fn_installations.Rmd
apm ex-mode :q :w, game tree continued

```{R}
.libPath()
# C:/Users/fan/Documents/R/win-library/3.6
# C:/Program Files/R/R-3.6.1/library
```

@@

# vim distraction free editing
apm install vim-mode-plus
apm install zen

>>>>

```{r}
.libPath()
# C:/Users/fan/Documents/R/win-library/3.6
# C:/Program Files/R/R-3.6.1/library
```

@@

# vim distraction free editing
apm install vim-mode-plus
apm install ex-mode
apm install zen
